Declarative Deployment Reconfiguration of Pulverised Collective Adaptive Systems at Runtime \thanks{ This work has been supported by the Italian PRIN Project COMMON-WEARS (2020HCWWLP) and the EU/MUR FSE REACT-EU PON R\&I 2014-2020. }

### 2023-05-18 paper-2023-acsos-pulverization.tex
Add power consumption model description

>>>>

\meta{
The simulation of this large-scale scenario should take into account several factors to be more realistic as possible:
the power consumption of the werable devices (smartphones), the power consumption of the cloud server,
and the weight of the application in terms of power dissipated by its execution.
%
The parameter described above represent the fundamental element of the power consumption model used in the simulation.
%
To be more adeherent as possible to a real consumption model of a device or cloud server,
several research were conducted to figure out real value that can be used as parameter in the simulation.
%
Nevertheless,
for our bes of knowledge,
there are no precise and established studies regarding these specific parameters.
%
For this reason,
we tried to identify likelihood parameters that could describe a plausible scenario in simulation.
%
In the following, we describe the parameters used in the simulation and the motivation behind their choice.
%
One popular metrics which relate the power consumption with the instruction is the \emph{Energy Per Instruction}
(EPI)~\cite{Grochowski2006EnergyPI} measured in $J / instruction$,
which associate the energy related to the execution of a CPU instruction.
%
From the metric introduced above, we should estimate the $EPI_{cloud}$ and $EPI_{device}$.
%
To do so, we rely our estimation based on the result obtained in~\cite{DBLP:conf/islped/ShaoB13},
were the EPI of a server CPU is calculated.
%
From the value taken from~\cite{DBLP:conf/islped/ShaoB13} we defined a discrete variability range for
$EPI_{cloud}$ equals to $300$, $30$, and $3$.
%
To estimate the $EPI_{device}$,
an intermediate step could be determine the ratio between $EPI_{cloud}$ and $EPI_{device}$,
which we define as $EPI_{ratio}$.
%
To do so we could rely on other characterizing elements:
the \emph{TDP} of each CPU and the \emph{benchmark score} of each CPU,
and for each one,
define the ratio of this two metrics: $TDP_{ratio}$ and $Benachmark_{ratio}$.
%
In this way we are identifying the power ration and performance ratio between the CPU of the device
and the CPU of the cloud.
%
The $EPI_{ratio}$ now can be define as:
$$EPI_{ratio} = \frac{TDP_{ratio}}{Benchmark_{ratio}}$$
%
Supposing to have smartphones with the \emph{Snapdragon 888} (5W TDP) as a CPU and a cloud server
with an \emph{Intel Xeon W-3375} (220W TDP), the respective benchmark results are $59,069$ and $9,362$.
%
Consequently, the $EPI_{ratio}$ is near to $7$.
%
To mitigate the uncertainty of this values we ranged the $EPI_{ratio}$ from 3 to 30.
%
The simulation consist of several scenarios in which we simulate different application load,
and consequently different discharge time of the devices.
%
To do so, we estimate the number of instruction based on
the $EPI_{device}$ and the required discharge time to simulate.
%
Given the total instruction of our application,
we repartition that value for each component executed and the relative communication cost;
in this way,
we can estimate the consumption of each component either executed in cloud or in device.
%
The power consumption is trivially determined by:
$$P = \frac{instructions * EPI}{time}$$
where \emph{time} is the time interval between two measure,
that in the simulation corresponds to the delta time between two simulation steps.
}
